Analytic Occultation Light Curves in Reflected Light

### 2020-04-16 tex/ms.tex
fixed p2

\subsection{Review of the \starry algorithm in emitted light}
\label{sec:starry-review}
%
Without loss of generality, assume the body whose flux we wish to compute
has radius unity and sits at the origin of a right-handed Cartesian coordinate
system in some frame $\mathcal{F}_0$. In this frame,
the surface (emitted) intensity field of the body is described by a
vector $\mathbf{y}$ of coefficients in the spherical harmonic
basis $\by$:
%
\begin{align}
    \label{eq:by}
    \by & =
    \begin{pmatrix}
        Y_{0, 0}  &
        Y_{1, -1} & Y_{1, 0}  & Y_{1, 1} &
        Y_{2, -2} & Y_{2, -1} & Y_{2, 0} & Y_{2, 1} & Y_{2, 2} &
        \cdot\cdot\cdot
    \end{pmatrix}^\top
    \quad,
\end{align}
%
where the component at index $n$ is $Y_{l,m}$ with
%
\begin{align}
    \label{eq:l-m}
    l & = \floor*{\sqrt{n}}
    \nonumber               \\
    m & = n - l^2 - l
    \quad.
\end{align}
%
An observer views the body from a large distance in the sky frame
$\mathcal{F}$, in which the $x$-axis points to the right,
the $y$-axis points up, and the $z$-axis points out of the sky
toward the observer. Following \citet{Luger2019}, if
an occultor of radius $r_o$ is located at sky position $(x_o, y_o)$,
we compute the visible flux $f$ from
%
\begin{align}
    \label{eq:sTARRy}
    f = \sTe \mathbf{A} \mathbf{R}' \mathbf{R} \mathbf{y}
    \quad,
\end{align}
%
where, from right to left, $\mathbf{R} = \mathbf{R}(i, \lambda, \vartheta)$
is a Wigner rotation matrix that rotates $\bvec{y}$ from $\mathcal{F}_0$
to the sky frame $\mathcal{F}$
given the body's inclination $i$, obliquity
$\lambda$, and rotational phase $\vartheta$
\citep[Appendix C in][]{Luger2019},
%
$\mathbf{R}' = \mathbf{R}'(x_o, y_o)$ rotates the body on the plane
of the sky into the integration frame $\mathcal{F}'$, in which the
occultor lies along the $+y'$-axis,
%
$\mathbf{A}$
\citep[Equation~B13 in][]{Luger2019}
is the change-of-basis matrix from $\by$
to the \emph{Green's basis} $\bg$ in which the integrals are computed,
whose component at index $n$ is
%
\begin{align}
    \label{eq:bg}
    \tilde{g}_{n}(x, y) & =
    \begin{dcases}
        %
        \frac{\mu+2}{2}x^\frac{\mu}{2} y^\frac{\nu}{2}
         & \qquad \mu, \nu \, \text{even}
        \\[1em]
        %
        z(x, y)
         & \qquad \mu = \nu = 1
        \\[1em]
        %
        3x^{l-2}yz(x, y)
         & \qquad \nu \, \text{odd}, \,
        \mu = 1, \,
        \frac{\mu + \nu}{2} \, \text{even}
        \\[1em]
        %
        z(x, y)
        \bigg(
        -x^{l-3} + x^{l-1} + 4x^{l-3}y^2
        \bigg)
         & \qquad \nu \, \text{odd}, \,
        \mu = 1, \,
        \, \text{odd}
        \\[1em]
        %
        z(x, y)
        \bigg(
        \frac{\mu-3}{2} x^\frac{\mu-5}{2} y^\frac{\nu-1}{2}
        \ - \
        \frac{\mu-3}{2} x^\frac{\mu-5}{2} y^\frac{\nu+3}{2}
        \\
        \qquad\qquad \ - \
        \frac{\mu+3}{2} x^\frac{\mu-1}{2} y^\frac{\nu-1}{2}
        \bigg)
         & \qquad \text{otherwise}
        \quad,
    \end{dcases}
\end{align}
%
with
%
\begin{align}
    \label{eq:mu-nu}
    \mu & \equiv l - m
    \nonumber          \\
    \nu & \equiv l + m
\end{align}
%
and
%
\begin{align}
    z(x, y) \equiv \sqrt{1 - x^2 - y^2}
    \quad,
\end{align}
%
and $\sTe = \sTe(b_o, r_o)$ is the vector of solutions to the integral over
the projected visible disk of the body for each term in $\bg$
\citep[Equation~26 in][]{Luger2019}, with $b_o = \sqrt{x_o^2 + y_o^2}$.

@@

\subsection{Computing the integrals $\sT$}
\label{sec:sT}
%
In the previous sections, we discussed how to identify the case
corresponding to a specific configuration of the occultor and the
illumination source. We showed how in some cases
(1--5; \S\ref{sec:cases-easy}) the total flux may be
computed by exploiting the classical \starry integrals (Equation~\ref{eq:fI}).
In all other cases (6--14; \S\ref{sec:cases-hard} and
\S\ref{sec:cases-pathological}), however, the flux computation involves
evaluation of
Equation~(\ref{eq:fS}), where the solution vector $\sT$
is the vector of integrals (in the frame $\mathcal{F}'$)
of each of the terms in the Green's basis $\bg$
over a region $S$ of the
projected disk of the occultor (Equation~\ref{eq:sTint}).
%
As in \citet{Luger2019}, the approach to computing $\sT$
is to use Green's theorem to transform the surface integrals into line
integrals along the curves $\mathcal{P}$, $\mathcal{T}$, and $\mathcal{Q}$
(see Figure~\ref{fig:geometry}). Specifically, we write%
\footnote{%
    In this section, we deliberately drop the dependence of $\sT$ and
    the primitive
    integrals on the geometrical parameters $b, \theta', b_o, r_o$
    for clarity.
}
%
\begin{align}
    \label{eq:greens}
    \sT
     & =
    \iint\limits_{S}
    \bg^\top(x', y')
    \ \dd x' \ \dd y'
    \nonumber \\[0.5em]
     & =
    \oint \bvec{G}^\top (x', y') \cdot
    \dd \bvec{r} (x', y')
    \quad,
\end{align}
%
where $\bvec{G} (x', y')$
is a vector of two-dimensional Cartesian vectors chosen such that its
exterior derivative is $\bg$,
%
\begin{align}
    \label{eq:DGg}
    \frac{\dd \bvec{G}_{y'}(x', y')}{\dd x'}
    - \frac{\dd \bvec{G}_{x'}(x', y')}{\dd y'} = \bg(x', y')
    \quad,
\end{align}
%
and
%
\begin{align}
    \dd \mathbf{r} (x', y') & =
    \left(\frac{\dd x'}{\dd \varphi}\right) \dd \varphi \, \xhat' +
    \left(\frac{\dd y'}{\dd \varphi}\right) \dd \varphi \, \yhat'
    \quad,
\end{align}
%
where $\varphi$ is the parametrized angle along the integration path
and the integral is taken in a counter-clockwise direction relative to
the center of the integration region.
%
\citet{Luger2019} showed that one possible solution to
Equation~(\ref{eq:DGg}) consists of the vector whose $n^\text{th}$
component is given by
%
\begin{align}
    \label{eq:G}
    \mathbf{G}_n (x, y) & =
    \begin{dcases}
        %
        x'^{\frac{\mu + 2}{2}}
        y'^{\frac{\nu}{2}}
        \,\yhat'
         & \qquad \mu, \nu \, \text{even}
        \\[1em]
        %
        \frac{1-z(x', y')^3}{3(1-z(x', y')^2)}\bigg(-y' \, \xhat' + x' \, \yhat'\bigg)
         & \qquad \mu = \nu = 1
        \\[1em]
        %
        x'^{l-2}
        z(x', y')^3
        \,\xhat
         & \qquad \nu \, \text{odd}, \,
        \mu = 1, \,
        l \, \text{even}
        \\[1em]
        %
        x'^{l-3}
        y'
        z(x', y')^3
        \,\xhat
         & \qquad \nu \, \text{odd}, \,
        \mu = 1, \,
        l \, \text{odd}
        \\[1em]
        %
        x'^{\frac{\mu-3}{2}}
        y'^{\frac{\nu-1}{2}}
        z(x', y')^3
        \,\yhat
         & \qquad \text{otherwise,}
    \end{dcases}
\end{align}
%
where the indices $l, m, \mu, \nu$ are given by Equation~(\ref{eq:l-m-mu-nu}).

@@

\subsubsection{The vector $\viI$}
\label{sec:I}
%
The components of the vector $\viI$ are given by the integral
%
\begin{align}
    \label{eq:I}
    \iI_v(\vkappa) & =
    \vint{\vkappa}{\sinhalfkap[2v]}
    \quad,
\end{align}
%
for $v \in [0, \vmax]$,
where we define the helper angle
%
\begin{align}
    \label{eq:kappa}
    \pmb{\kappa} = \pmb{\phi} + \frac{\pi}{2}
    \quad.
\end{align}
%
The integral in the expression above is the same as that in Equation (D38)
of \citet{Luger2019}, except for a change in the limits of integration.
As in \citet{Luger2019}, we can compute the vector $\viI$ recursively given
a trivial lower boundary condition:
%
\begin{proof}{I}
    \label{eq:Irec}
    \iI_0(\vkappa) &=
    \frac{\Delta \vkappa}{2}
    %
    \nonumber \\
    %
    \iI_v(\vkappa) &=
    \frac{1}{2v}
    \bigg(
    (2v - 1) \iI_{v-1}(\vkappa) -
    \Delta \left(\sinhalfkap[2v - 1]\coshalfkap\right)
    \bigg)
\end{proof}
%
where the last expression is valid for all $v > 0$. We find that this algorithm
is generally stable, except when
$\sin\left(\nicefrac{\vkappa}{2}\right)$ is small.
In that limit, we evaluate $\iI_\vmax(\vkappa)$
by numerical integration of
Equation~(\ref{eq:I}) using Gauss-Legendre quadrature with \STARRYQUADPOINTS
points. We then recurse downward by substituting $v \rightarrow v + 1$ in
Equation~(\ref{eq:Irec}) and solving for $\iI_v(\vkappa)$.

\subsubsection{The vector $\viJ$}
\label{sec:J}
%
The components of the vector $\viJ$ are given by the integral
%
\begin{align}
    \label{eq:J}
    \iJ_v(k^2, \vkappa) =
    \vint{\vkappa}{
        \sin^{2v}\varphi
        \left(1 - \frac{\sin^2\varphi}{k^2}\right)^\frac{3}{2}
    }
    \quad.
\end{align}
%
\xxx{Define $k^2$.}
The integral in this expression is again the same as that in Equation (D39)
of \citet{Luger2019}, except for a change in the limits of integration.
In that paper, we computed all terms
$\{ \iJ_0, {\cdot\cdot\cdot}, \iJ_\vmax \}$ from a three-term
recurrence relation and two boundary conditions. In the case of upward
recursion, the boundary conditions $\iJ_0$ and $\iJ_1$ were
computed analytically from the complete elliptic integrals $K(k^2)$
and $E(k^2)$. In cases where upward recursion was not numerically stable, we
evaluated $\iJ_\vmax$ and $\iJ_{\vmax-1}$
via a quickly convergent series expansion and recursed downward.

In order to solve Equation~(\ref{eq:J}), it is possible to
replace the complete elliptic integrals $K(k^2)$ and $E(k^2)$ in the lower
boundary conditions \citep[Equation D46 in ][]{Luger2019} with the
incomplete elliptic integrals
%
\begin{align}
    \label{eq:F}
    \mathbb{F}(k^2, \kappa) & = \int_0^{\kappa} \frac{\dd \varphi}{\sqrt{1 - k^2 \sin^2 \varphi}}
    \\
    \intertext{and}
    \label{eq:E}
    \mathbb{E}(k^2, \kappa) & = \int_0^{\kappa} \sqrt{1 - k^2 \sin^2 \varphi} \, \dd \varphi
\end{align}
%
then use the same upward
recursion relation to obtain analytic solutions for all $\iJ_v$:
%
\begin{proof}{J}
    \label{eq:Jrec}
    \iJ_0(k^2, \vkappa) &=
    \frac{1}{3} \bigg(
    2 \left(2 - \frac{1}{k^2}\right) \DE +
    \left(\frac{1}{k^2} - 1\right) \DF +
    \Delta \mathbf{z}_0(k^2, \vkappa)
    \bigg)
    %
    \nonumber \\
    %
    \iJ_1(k^2, \vkappa) &=
    \frac{1}{15} \bigg(
    \left(-3 k^2 + 13 - \frac{8}{k^2}\right) \DE +
    \nonumber \\
    &\qquad\quad\quad\quad\quad\quad\quad\quad\quad
    \left(3 k^2 - 7 + \frac{4}{k^2}\right) \DF +
    \Delta \mathbf{z}_1(k^2, \vkappa)
    \bigg)
    %
    \nonumber \\
    %
    \iJ_v(k^2, \vkappa) &=
    \frac{1}{2v + 3}
    \bigg(
    2 \left( v + 1 + (v - 1) k^2 \right) \iJ_{v - 1} -
    (2v - 3) k^2 \iJ_{v - 2}
    + \Delta \mathbf{z}_v(k^2, \vkappa)
    \bigg)
\end{proof}
%
%
where the last expression is valid for all $v > 1$ and
%
\begin{proof}{J}
    \label{eq:Jrec_z}
    \mathbf{z}_0(k^2, \pmb{\kappa}) & =
    \frac{
        \sinhalfkap
        \coshalfkap
        \mathbf{q}(k^2, \vkappa)
    }{
        k^2
    }
    %
    \nonumber\\
    %
    \mathbf{z}_1(k^2, \pmb{\kappa}) & =
    \left(\left(3 \sinhalfkap[2] + 4\right) - 6k^2\right)
    \mathbf{z}_0(k^2, \pmb{\kappa})
    %
    \nonumber\\
    %
    \mathbf{z}_v(k^2, \pmb{\kappa}) & =
    k^2
    \sinhalfkap[2v - 3]
    \coshalfkap
    \mathbf{q}(k^2, \pmb{\kappa})^5
    \quad,
\end{proof}
%
with
%
\begin{align}
    \label{eq:q}
    \mathbf{q}(k^2, \vkappa) = \sqrt{1 - \frac{\sinhalfkap[2]}{k^2}}
    \quad.
\end{align}
%
However, in practice we find that this procedure is even more numerically
unstable than it was in \citet{Luger2019}.
To address this, we express the recurrence structure of the problem as
a tridiagonal system with one lower boundary condition $\iJ_0$
and one upper boundary condition $\iJ_\vmax$:
%
\begin{proof}{J}
    \label{eq:Jtri}
    \begin{pmatrix}
        a_0 & 1   &     &        &         &         \\
        b_1 & a_1 & 1   &        &         &         \\
            & b_2 & a_2 & 1      &         &         \\
            &     & b_0 & a_3    & 1       &         \\
            &     &     & \ddots & \ddots  & \ddots  \\
            &     &     &        & b_\vmax & a_\vmax
    \end{pmatrix}
    \begin{pmatrix}
        \iJ_1           \\
        \iJ_2           \\
        \iJ_3           \\
        \iJ_4           \\
        \cdot\cdot\cdot \\
        \iJ_{\vmax-1}
    \end{pmatrix}
    =
    \begin{pmatrix}
        c_0 - b_0 \iJ_0 \\
        c_1             \\
        c_2             \\
        c_3             \\
        \cdot\cdot\cdot \\
        c_\vmax - \iJ_\vmax
    \end{pmatrix}
\end{proof}
%
where the recursion coefficients are given by
%
\begin{proof}{J}
    \label{eq:Jtri_coeffs}
    a_v(k) &= -2\frac{(v + 1) + (v - 1) k^2}{2v + 3} \nonumber \\
    b_v(k) &= \frac{(2v - 3) k^2}{2v + 3} \nonumber \\
    c_v(k^2, \vkappa) &= \Delta
    \bigg(
    \frac{
            \mathbf{z}_v(k^2, \pmb{\kappa})
        }{
            2v + 3
        }
    \bigg)
    \quad.
\end{proof}
%
Solving this matrix system yields values for all
intermediate $\{ \iJ_1, {\cdot\cdot\cdot}, \iJ_{\vmax - 1} \}$.
While efficient algorithms exist for solving tridiagonal problems, we obtain
far better numerical stability by instead performing traditional LU
decomposition. We find that this algorithm is stable in all the regimes that we
tested.

@@

\subsubsection{The vector $\viU$}
\label{sec:U}
%
The components of the vector $\viU$ are given by the integral
%
\begin{align}
    \label{eq:U}
    \iU_v(\vkappa) =
    \vint{\vkappa}{\cos\varphi\sin^{2v}\varphi}
    \quad.
\end{align}
%
This integral has an analytic solution for all $v$:
%
\begin{proof}{U}
    \label{eq:Usol}
    \iU_v(\vkappa) &= \frac{\Delta \sinhalfkap[v+1]}{v + 1}
    \quad.
\end{proof}
%

>>>>

\subsection{Review of the \starry algorithm in emitted light}
\label{sec:starry-review}
%
Without loss of generality, assume the body whose flux we wish to compute
has radius unity and sits at the origin of a right-handed Cartesian coordinate
system in some frame $\mathcal{F}_0$. In this frame,
the surface (emitted) intensity field of the body is described by a
vector $\mathbf{y}$ of coefficients in the spherical harmonic
basis $\by$:
%
\begin{align}
    \label{eq:by}
    \by & =
    \begin{pmatrix}
        Y_{0, 0}  &
        Y_{1, -1} & Y_{1, 0}  & Y_{1, 1} &
        Y_{2, -2} & Y_{2, -1} & Y_{2, 0} & Y_{2, 1} & Y_{2, 2} &
        \cdot\cdot\cdot
    \end{pmatrix}^\top
    \quad,
\end{align}
%
where the component at index $n$ is $Y_{l,m}$ with
%
\begin{align}
    \label{eq:l-m}
    l & = \floor*{\sqrt{n}}
    \nonumber               \\
    m & = n - l^2 - l
    \quad.
\end{align}
%
An observer views the body from a large distance in the sky frame
$\mathcal{F}$, in which the $x$-axis points to the right,
the $y$-axis points up, and the $z$-axis points out of the sky
toward the observer. Following \citet{Luger2019}, if
an occultor of radius $r_o$ is located at sky position $(x_o, y_o)$,
we compute the visible flux $f$ from
%
\begin{align}
    \label{eq:sTARRy}
    f = \sTe \mathbf{A} \mathbf{R}' \mathbf{R} \mathbf{y}
    \quad,
\end{align}
%
where, from right to left, $\mathbf{R} = \mathbf{R}(i, \lambda, \vartheta)$
is a Wigner rotation matrix that rotates $\bvec{y}$ from $\mathcal{F}_0$
to the sky frame $\mathcal{F}$
given the body's inclination $i$, obliquity
$\lambda$, and rotational phase $\vartheta$
\citep[Appendix C in][]{Luger2019},
%
$\mathbf{R}' = \mathbf{R}'(x_o, y_o)$ rotates the body on the plane
of the sky into the integration frame $\mathcal{F}'$, in which the
occultor lies along the $+y'$-axis,
%
$\mathbf{A}$
\citep[Equation~B13 in][]{Luger2019}
is the change-of-basis matrix from $\by$
to the \emph{Green's basis} $\bg$ in which the integrals are computed,
whose component at index $n$ is
%
\begin{align}
    \label{eq:bg}
    \tilde{g}_{n}(x, y) & =
    \begin{dcases}
        %
        \frac{\mu+2}{2}x^\frac{\mu}{2} y^\frac{\nu}{2}
         & \qquad \mu, \nu \, \text{even}
        \\[1em]
        %
        z(x, y)
         & \qquad \mu = \nu = 1
        \\[1em]
        %
        3x^{l-2}yz(x, y)
         & \qquad \nu \, \text{odd}, \,
        \mu = 1, \,
        \frac{\mu + \nu}{2} \, \text{even}
        \\[1em]
        %
        z(x, y)
        \bigg(
        -x^{l-3} + x^{l-1} + 4x^{l-3}y^2
        \bigg)
         & \qquad \nu \, \text{odd}, \,
        \mu = 1, \,
        \, \text{odd}
        \\[1em]
        %
        z(x, y)
        \bigg(
        \frac{\mu-3}{2} x^\frac{\mu-5}{2} y^\frac{\nu-1}{2}
        \ - \
        \frac{\mu-3}{2} x^\frac{\mu-5}{2} y^\frac{\nu+3}{2}
        \\
        \qquad\qquad \ - \
        \frac{\mu+3}{2} x^\frac{\mu-1}{2} y^\frac{\nu-1}{2}
        \bigg)
         & \qquad \text{otherwise}
        \quad,
    \end{dcases}
\end{align}
%
with
%
\begin{align}
    \label{eq:mu-nu}
    \mu & \equiv l - m
    \nonumber          \\
    \nu & \equiv l + m
\end{align}
%
and
%
\begin{align}
    \label{eq:z}
    z(x, y) \equiv \sqrt{1 - x^2 - y^2}
    \quad,
\end{align}
%
and $\sTe = \sTe(b_o, r_o)$ is the vector of solutions to the integral over
the projected visible disk of the body for each term in $\bg$
\citep[Equation~26 in][]{Luger2019}, with $b_o = \sqrt{x_o^2 + y_o^2}$.

@@

\subsection{Computing the integrals $\sT$}
\label{sec:sT}
%
In the previous sections, we discussed how to identify the case
corresponding to a specific configuration of the occultor and the
illumination source. We showed how in some cases
(1--5; \S\ref{sec:cases-easy}) the total flux may be
computed by exploiting the classical \starry integrals (Equation~\ref{eq:fI}).
In all other cases (6--14; \S\ref{sec:cases-hard} and
\S\ref{sec:cases-pathological}), however, the flux computation involves
evaluation of
Equation~(\ref{eq:fS}), where the solution vector $\sT$
is the vector of integrals (in the frame $\mathcal{F}'$)
of each of the terms in the Green's basis $\bg$
over a region $S$ of the
projected disk of the occultor (Equation~\ref{eq:sTint}).
%
As in \citet{Luger2019}, the approach to computing $\sT$
is to use Green's theorem to transform the surface integrals into line
integrals along the curves $\mathcal{P}$, $\mathcal{T}$, and $\mathcal{Q}$
(see Figure~\ref{fig:geometry}). Specifically, we write%
\footnote{%
    In this section, we deliberately drop the dependence of $\sT$ and
    the primitive
    integrals on the geometrical parameters $b, \theta', b_o, r_o$
    for clarity.
}
%
\begin{align}
    \label{eq:greens}
    \sT
     & =
    \iint\limits_{S}
    \bg^\top(x', y')
    \ \dd x' \ \dd y'
    \nonumber \\[0.5em]
     & =
    \oint \bvec{G}^\top (x', y') \cdot
    \dd \bvec{r} (x', y')
    \quad,
\end{align}
%
where $\bvec{G} (x', y')$
is a vector of two-dimensional Cartesian vectors chosen such that its
exterior derivative is $\bg$,
%
\begin{align}
    \label{eq:DGg}
    \frac{\dd \bvec{G}_{y'}(x', y')}{\dd x'}
    - \frac{\dd \bvec{G}_{x'}(x', y')}{\dd y'} = \bg(x', y')
    \quad,
\end{align}
%
and
%
\begin{align}
    \dd \mathbf{r} (x', y') & =
    \left(\frac{\dd x'}{\dd \varphi}\right) \dd \varphi \, \xhat' +
    \left(\frac{\dd y'}{\dd \varphi}\right) \dd \varphi \, \yhat'
    \quad,
\end{align}
%
where $\varphi$ is the parametrized angle along the integration path
and the integral is taken in a counter-clockwise direction relative to
the center of the integration region.
%
\citet{Luger2019} showed that one possible solution to
Equation~(\ref{eq:DGg}) consists of the vector whose $n^\text{th}$
component is given by
%
\begin{align}
    \label{eq:G}
    \mathbf{G}_n (x', y') & =
    \begin{dcases}
        %
        x'^{\frac{\mu + 2}{2}}
        y'^{\frac{\nu}{2}}
        \,\yhat'
         & \qquad \mu, \nu \, \text{even}
        \\[1em]
        %
        \frac{1-z(x', y')^3}{3(1-z(x', y')^2)}\bigg(-y' \, \xhat' + x' \, \yhat'\bigg)
         & \qquad \mu = \nu = 1
        \\[1em]
        %
        x'^{l-2}
        z(x', y')^3
        \,\xhat
         & \qquad \nu \, \text{odd}, \,
        \mu = 1, \,
        l \, \text{even}
        \\[1em]
        %
        x'^{l-3}
        y'
        z(x', y')^3
        \,\xhat
         & \qquad \nu \, \text{odd}, \,
        \mu = 1, \,
        l \, \text{odd}
        \\[1em]
        %
        x'^{\frac{\mu-3}{2}}
        y'^{\frac{\nu-1}{2}}
        z(x', y')^3
        \,\yhat
         & \qquad \text{otherwise,}
    \end{dcases}
\end{align}
%
where the indices $l, m, \mu, \nu$ are given by Equation~(\ref{eq:l-m-mu-nu}).

@@

\subsubsection{The vector $\viI$}
\label{sec:I}
%
The components of the vector $\viI$ are given by the integral
%
\begin{align}
    \label{eq:I}
    \iI_v(\valpha) & =
    \vint{\valpha}{\sin^{2v}\varphi}
    \quad,
\end{align}
%
for $v \in [0, \vmax]$,
where we define the helper angle
%
\begin{align}
    \label{eq:alpha}
    \valpha \equiv \frac{\pmb{\phi}}{2} + \frac{\pi}{4}
    \quad.
\end{align}
%
The integral in the expression above is the same as that in Equation (D38)
of \citet{Luger2019}, except for a change in the limits of integration.
As in \citet{Luger2019}, we can compute the vector $\viI$ recursively given
a trivial lower boundary condition:
%
\begin{proof}{I}
    \label{eq:Irec}
    \iI_0(\valpha) &=
    \Delta \valpha
    %
    \nonumber \\
    %
    \iI_v(\valpha) &=
    \frac{1}{2v}
    \bigg(
    (2v - 1) \iI_{v-1}(\valpha) -
    \Delta \left(\sin^{2v - 1}\valpha\cos^{2v -1}\valpha\right)
    \bigg)
\end{proof}
%
where the last expression is valid for all $v > 0$. We find that this algorithm
is generally stable, except when
$\sin\valpha$ is small.
In that limit, we evaluate $\iI_\vmax(\valpha)$
by numerical integration of
Equation~(\ref{eq:I}) using Gauss-Legendre quadrature with \STARRYQUADPOINTS
points. We then recurse downward by substituting $v \rightarrow v + 1$ in
Equation~(\ref{eq:Irec}) and solving for $\iI_v(\valpha)$.

\subsubsection{The vector $\viJ$}
\label{sec:J}
%
The components of the vector $\viJ$ are given by the integral
%
\begin{align}
    \label{eq:J}
    \iJ_v(k^2, \valpha) =
    \vint{\valpha}{
        \sin^{2v}\varphi
        \left(1 - \frac{\sin^2\varphi}{k^2}\right)^\frac{3}{2}
    }
    \quad,
\end{align}
%
where
%
\begin{align}
    \label{eq:k2}
    k^2 & \equiv \frac{1 - r_o^2 - b_o^2 + 2 b_o r_o}{4 b_o r_o}
    \quad.
\end{align}
%
The integral in this expression is again the same as that in Equation (D39)
of \citet{Luger2019}, except for a change in the limits of integration.
In that paper, we computed all terms
$\{ \iJ_0, {\cdot\cdot\cdot}, \iJ_\vmax \}$ from a three-term
recurrence relation and two boundary conditions. In the case of upward
recursion, the boundary conditions $\iJ_0$ and $\iJ_1$ were
computed analytically from the complete elliptic integrals $K(k^2)$
and $E(k^2)$. In cases where upward recursion was not numerically stable, we
evaluated $\iJ_\vmax$ and $\iJ_{\vmax-1}$
via a quickly convergent series expansion and recursed downward.

In order to solve Equation~(\ref{eq:J}), it is possible to
replace the complete elliptic integrals $K(k^2)$ and $E(k^2)$ in the lower
boundary conditions \citep[Equation D46 in ][]{Luger2019} with the
incomplete elliptic integrals
%
\begin{align}
    \label{eq:F}
    \mathbb{F}(\psi \,|\, m) & \equiv \int_0^{\psi} \frac{\dd \varphi}{\sqrt{1 - m \sin^2 \varphi}}
    \\
    \intertext{and}
    \label{eq:E}
    \mathbb{E}(\psi \,|\, m) & \equiv \int_0^{\psi} \sqrt{1 - m \sin^2 \varphi} \, \dd \varphi
    \quad,
\end{align}
%
which we compute from the $el\mathit{2}$ parametrization of
\citet{Bulirsch1965},
%
then use the same upward
recursion relation to obtain analytic solutions for all $\iJ_v$:
%
\begin{proof}{J}
    \label{eq:Jrec}
    \iJ_0(k^2, \valpha) &=
    \frac{1}{3} \bigg(
    2 \left(2 - \frac{1}{k^2}\right) \DE +
    \left(\frac{1}{k^2} - 1\right) \DF +
    \Delta \mathbf{z}_0(k^2, \valpha)
    \bigg)
    %
    \nonumber \\
    %
    \iJ_1(k^2, \valpha) &=
    \frac{1}{15} \bigg(
    \left(-3 k^2 + 13 - \frac{8}{k^2}\right) \DE
    \nonumber \\
    &\qquad\quad\quad\quad\quad\quad\quad\quad\quad
    +
    \left(3 k^2 - 7 + \frac{4}{k^2}\right) \DF +
    \Delta \mathbf{z}_1(k^2, \valpha)
    \bigg)
    %
    \nonumber \\
    %
    \iJ_v(k^2, \valpha) &=
    \frac{1}{2v + 3}
    \bigg(
    2 \left( v + 1 + (v - 1) k^2 \right) \iJ_{v - 1}(k^2, \valpha)
    \nonumber \\
    &\qquad\qquad\quad\quad\quad\quad
    -
    (2v - 3) k^2 \iJ_{v - 2}(k^2, \valpha)
    + \Delta \mathbf{z}_v(k^2, \valpha)
    \bigg)
\end{proof}
%
%
where the last expression is valid for all $v > 1$ and
%
\begin{proof}{J}
    \label{eq:Jrec_z}
    \mathbf{z}_0(k^2, \valpha) & =
    \frac{
        \sin\valpha
        \cos\valpha
        \,
        \mathbf{q}(k^2, \valpha)
    }{
        k^2
    }
    %
    \nonumber\\
    %
    \mathbf{z}_1(k^2, \valpha) & =
    \left(3 \sin^2\valpha + 4 - 6k^2\right)
    \mathbf{z}_0(k^2, \valpha)
    %
    \nonumber\\
    %
    \mathbf{z}_v(k^2, \valpha) & =
    k^2
    \sin^{2v - 3}\valpha
    \cos\valpha
    \,
    \mathbf{q}(k^2, \valpha)^5
    \quad,
\end{proof}
%
with
%
\begin{align}
    \label{eq:q}
    \mathbf{q}(k^2, \valpha) = \sqrt{1 - \frac{\sin^2\valpha}{k^2}}
    \quad.
\end{align}
%
Note that when $k^2 < 1$ we use the reciprocal-modulus transformation
to evaluate the elliptic integrals:
%
\begin{align}
    \mathbb{F}\left(\psi \,\Big|\, \frac{1}{k^2}\right) & =
    k \, \mathbb{F}(\beta \,|\, k^2)
    \nonumber                                                                                        \\
    \mathbb{E}\left(\psi \,\Big|\, \frac{1}{k^2}\right) & =
    \frac{\mathbb{E}(\beta \,|\, k^2) - (1 - k^2) \mathbb{F}(\beta \,|\, k^2)}{k}
    \\
    \intertext{with}
    \beta                                               & = \arcsin\left( \frac{\sin\psi}{k} \right)
    \quad.
\end{align}
%

In practice, however, we find that this procedure is even more numerically
unstable than it was in \citet{Luger2019}.
To address this, we express the recurrence structure of the problem as
a tridiagonal system with one lower boundary condition $\iJ_0$
and one upper boundary condition $\iJ_\vmax$:
%
\begin{proof}{J}
    \label{eq:Jtri}
    \begin{pmatrix}
        a_0 & 1   &     &        &         &         \\
        b_1 & a_1 & 1   &        &         &         \\
            & b_2 & a_2 & 1      &         &         \\
            &     & b_0 & a_3    & 1       &         \\
            &     &     & \ddots & \ddots  & \ddots  \\
            &     &     &        & b_\vmax & a_\vmax
    \end{pmatrix}
    \begin{pmatrix}
        \iJ_1           \\
        \iJ_2           \\
        \iJ_3           \\
        \iJ_4           \\
        \cdot\cdot\cdot \\
        \iJ_{\vmax-1}
    \end{pmatrix}
    =
    \begin{pmatrix}
        c_0 - b_0 \iJ_0 \\
        c_1             \\
        c_2             \\
        c_3             \\
        \cdot\cdot\cdot \\
        c_\vmax - \iJ_\vmax
    \end{pmatrix}
\end{proof}
%
where the recursion coefficients are given by
%
\begin{proof}{J}
    \label{eq:Jtri_coeffs}
    a_v(k) &= -2\frac{(v + 1) + (v - 1) k^2}{2v + 3} \nonumber \\
    b_v(k) &= \frac{(2v - 3) k^2}{2v + 3} \nonumber \\
    c_v(k^2, \valpha) &= \Delta
    \bigg(
    \frac{
            \mathbf{z}_v(k^2, \valpha)
        }{
            2v + 3
        }
    \bigg)
    \quad.
\end{proof}
%
Solving this matrix system yields values for all
intermediate $\{ \iJ_1, {\cdot\cdot\cdot}, \iJ_{\vmax - 1} \}$.
While efficient algorithms exist for solving tridiagonal problems, we obtain
far better numerical stability by instead performing traditional LU
decomposition. We find that this algorithm is stable in all the regimes that we
tested.

@@

\subsubsection{The vector $\viU$}
\label{sec:U}
%
The components of the vector $\viU$ are given by the integral
%
\begin{align}
    \label{eq:U}
    \iU_v(\valpha) =
    \vint{\valpha}{\cos\varphi\sin^{2v + 1}\varphi}
    \quad.
\end{align}
%
This integral has an analytic solution for all $v$:
%
\begin{proof}{U}
    \label{eq:Usol}
    \iU_v(\valpha) &= \frac{\Delta \sin^{2v+2}\valpha}{2v + 2}
    \quad.
\end{proof}
%
